
\documentclass[journal]{IEEEtran}
\usepackage{amsthm}
\usepackage{url}
\usepackage{graphicx}

\begin{document}

\title{ PROPOSAL DOCUMENT }

\author{
\Large{Sameer Arora}\\
2016csb1058@iitrpr.ac.in
}

\large{
\tableofcontents
}
\maketitle

\begin{abstract}
In this report I want to decsribe a problem and its proposed solution.As we all know that for various government jobs,applications for institutions and many other services for the government are needed to get the applicants to upload there credentials on the internet and it consumes a lot of server space and a time from the user when he has to apply for various differet programmes. 
\end{abstract}

\section{Introduction}
 While applying for different recruitments through online application softcopy uploading of documents like educational qualification, D.O.B proof, category certificate etc. of candidate is required.This result in unnecessary utilization of server space as each application requires approximate 2MB storage space and thousands of applications are received.If credentials are verified then and there at the time of application receiving (uploading), it will be beneficial for all stakeholders.Moreover if the details required for the forms are available through the pictures itself using image processing and computer vision.
 
\section{IMPLEMENTATION DETAILS}
We can surely solve this problem by having a single database for each in indiviusual for the caste certificates,D.O.B certificates and other essential detais required folr that particular situation and can give the applicant a choice to fill the details manually or upload the images of documents needed and verify the details filled by the website.
\begin{itemize}
\item We can use the state of the art techniques already present for the computer vision and indentifiying various details required for the forms.
\item We can create a dummy database for just the demonstration and implement the website for that.
\item The forms can be customized as to which fields we want to get details from the images itself. 
\item The details declared as essential for the credibility of the applicant can be verified at that instant itself.
\end{itemize}
  
\section{Impacts on the society!}
\begin{itemize}
\item  It will be very easy for the applicants as now they need not waste their time in filling out all those obvious details.
\item It will save a lot of the server space and be very crucial for the space mangement.
\item It can be used by any similar kind of activity which requires details of the applicants .  
\end{itemize}

\section{Technology Stack}
For this project estimated tools needed for the project are listed below:-
\begin{itemize}
\item PHP for handling the forms and the server side.
\item MySQL for handling the datbases needed.
\item HTML,CSS and Javascript for front end development of the website.
\item OpenCV for using the computer vision,image processing and related features.
\item Maybe more to be discovered. 
\end{itemize}

\begin{thebibliography}{9}
\bibitem{website} 
I have reffered to the following website for getting a hint about the project.\\
\url{https://innovate.mygov.in/sih_ps/}
\end{thebibliography}
 
\end{document}
